# Detect languages

```{r}
library(data.table)
library(RMySQL)
library(cldr) # language identification based on Google library
library(wordcloud)

options(stringsAsFactors=FALSE)
```

Courses
```{r}
courses <- c("abed", "intropsych")
```

Set up database
```{r}
con <- dbConnect(MySQL(), user="root", password="passwd", host="127.0.0.1")
dbGetQuery(con, "SET NAMES utf8")
```

Function: Get tables 
```{r}
getMultipleTables <- function(connection, courses, table, remove=NULL) {
  db <- lapply(courses, function(x) {
    table <- paste0(x, ".", table)
    fp <- dbReadTable(connection, table)
    if(!is.null(remove)) { fp[[remove]] <- NULL}
    fp$course <- x
    fp
  })

  db2 <- rbindlist(db)
  db2
}
```

Read in and combine posts and comments, tagged by course provenance
```{r}
forum_posts <- getMultipleTables(con, courses, "forum_posts")
fp <- forum_posts[,list(forum_user_id, post_text, course)]
fp$text <- fp$post_text

forum_comments <- getMultipleTables(con, courses, "forum_comments",
                                    remove="thread_id")

cp <- forum_comments[,list(forum_user_id, comment_text, course)]
cp$text <- cp$comment_text

db <- rbind(cp[,list(forum_user_id,text, course)], 
            fp[,list(forum_user_id, text, course)])

db$id <- 1:nrow(db)
```

Clean up (save memory)
```{r}
cp <- NULL
forum_comments <- NULL
forum_posts <- NULL
fp <- NULL
```

Determine language - function
```{r}
determine_language <- Vectorize(function(x) { 
  c <- detectLanguage(x, includeExtendedLanguages=T)
  if(c$textBytes > 50) { return(c$detectedLanguage) } else { return(NA) }
})
```

Determine language (this could take a while! TODO: parallelize)
```{r}
db$lang <- determine_language(db$text)
db$lang <- as.factor(db$lang)
db[lang == "TG_UNKNOWN_LANGUAGE", lang := NA_character_]
db[lang != "ENGLISH" & !is.na(lang), foreign := T]
```

Now we have a table with comments and posts, tagged by course, and language. We can do all kinds of things with this, but for now let's do some quick overview stats.

How many foreign posts by course?
```{r}
prop.table(table(db$course, db$foreign))
```

Top languages overall
```{r}
langcnt <- data.frame(table(db$lang))
langordered <- langcnt[order(langcnt$Freq, decreasing=T),]
langordered[1:10,]
```

Let's look at comments in Indonesian
```{r}
db[db$lang == "INDONESIAN",]$text
wordcloud(words=db[db$lang == "INDONESIAN",]$text)
```